\documentclass[10.5pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in,headsep=0.2in]{geometry}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{fontawesome}

\nofiles{}

\usepackage{xcolor}
\definecolor{cpgreen}{HTML}{154734}
\definecolor{cpgold}{HTML}{C69214}

\newcolumntype{?}{!{\color{cpgreen}\vrule width \headrulewidth}}

\setlength{\columnsep}{10pt}

\fancypagestyle{resumeheader}{%
  \fancyhf{}%
  \fancyhead[EOL]{%
    {\color{cpgreen}
    \begin{minipage}[c][40pt][c]{0.44\textwidth}
      \huge\textbf{Jonathan Prentice}
    \end{minipage}
    }
  }
  \fancyhead[EOR]{%
    {%
    \begin{minipage}[r][40pt][c]{0.41\textwidth}
      \begin{tabular}{l ? l}
        \color{cpgreen}{\raisebox{-0.1em}{\faPhone}} (949) 438~\textemdash~8855 & \color{cpgreen}{\faEnvelope} japrenti@calpoly.edu \\
        \color{cpgreen}{\raisebox{-0.1em}{\faGithub}} github.com/jon77p & \color{cpgreen}{\faLinkedinSquare} linkedin.com/in/jon77p \\
      \end{tabular}
    \end{minipage}
    }
  }
  \fancyfoot[EO]{\vspace{45pt}}
  \renewcommand{\headrulewidth}{2pt}
  \setlength{\headheight}{0.7in}
  \setlength{\footskip}{55pt}
  \renewcommand{\headrule}{\hbox to\headwidth{\color{cpgreen}\leaders\hrule height \headrulewidth\hfill}}
}

\setlength{\columnsep}{10pt}

\setlist[itemize]{noitemsep, topsep=0pt, rightmargin=0.2in}

\newcommand{\resumesection}[2]{
  \vspace{1em}
  \noindent\Large{\textbf{#1}}\hfill\normalsize{#2}
}

\newcommand{\resumelistitem}[1]{
  \item{\normalsize{#1}}
}

\newcommand{\resumejobtitle}[5]{
  \vspace{0.6em}
  \noindent\large{\textbf{#1, \textit{#2} (#3)}}\hfill\normalsize{#4\textemdash#5}
}

\renewcommand{\labelitemi}{\color{cpgreen}\scriptsize\raisebox{0.25em}{$\bullet$}}

\begin{document}
  \pagestyle{resumeheader}

  \resumesection{Education}{~}

    \indent\textbf{California Polytechnic State University (Cal Poly), San Luis Obispo (SLO)}

    \indent\indent\small{B.S. Computer Science, concentrating in Security}\hfill\normalsize{Graduation: June 2021}

  \resumesection{Work Experience}{~}

    \resumejobtitle{Software Development Engineer Intern (Security)}{GoDaddy}{Remote}{June}{September 2020}

    \begin{itemize}
      \setlength{\itemsep}{0.15pt}
      \resumelistitem{Automated processes for on-demand analysis/reporting of CVE exploit exposure of potentially-affected machines within GoDaddy's infrastructure.}
      \resumelistitem{Utilized Mitre ATT\&CK's STIX implementation to relate
        techniques, tactics, and mitigations with relevant CVE
        exploits and their supporting classifications/weaknesses in Go.}
      \resumelistitem{Created a Go library to retrieve detailed information for
        CVEs, CPEs, and CAPECs using APIs for NIST and CIRCL.}
      \resumelistitem{Enriched IP and domain-related IOCs using Shodan data for internal team tools.}
    \end{itemize}

    \resumejobtitle{Junior Security Operations Center Analyst}{Cal Poly}{SLO}{October 2019}{Present}

    \begin{itemize}
      \setlength{\itemsep}{0.15pt}
      \resumelistitem{Triaged student, faculty, and staff-submitted phishing emails and suspicious user account network activity for blue-team tasks.}
      \resumelistitem{Achieved proficiency in Splunk by creating alerts, advanced dashboards, and workflows and completed \\ Splunk Fundamentals I.}
      \resumelistitem{Automated a Python script to parse, enrich, and normalize email files and IOCs to streamline daily analysis processes.}
    \end{itemize}

    \resumejobtitle{Threat Research Intern}{BlackBerry Cylance Inc.}{Irvine, CA}{June}{September 2019}

    \noindent\small\textit{Stuart McClure~\textemdash~CEO Executive Circle Summer Internship Program}\hfill\normalsize{June\textemdash September 2018}

    \begin{itemize}
      \setlength{\itemsep}{0.15pt}
      \resumelistitem{Developed an advanced automation framework to validate and test team-developed EDR rules against malicious and trusted binaries, and integrated it into the team's Jira workflow.}
      \resumelistitem{Created an EDR rule validation tool using Python for team usage and to validate consumer submissions.}
      \resumelistitem{Contributed towards mitigating the MITRE ATT\&CK Framework and secured high-priority company deals with custom EDR rules.}
      \resumelistitem{Learned advanced static and dynamic malware analysis skills and techniques and Metasploit hacking skills.}
      \resumelistitem{Enriched malicious hashes with family classification data using VirusTotal and internal APIs.}
		\end{itemize}

  \resumesection{Skills}{~}

    \vspace{0.6em}
    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l l l l}
        Security Automation & Splunk & Splunk Phantom & Malware Analysis \\
        Python & C & Go & Regex \\
        REST APIs & Web Scraping & x86 Reverse Engineering & Metasploit \\
        pfSense & VLANs & Firewall Administration & Computer Networking \\
        BASH/ZSH & vim & git & \LaTeX \\
        Python Flask & VMware & Docker & \texttt{systemd} \\
    \end{tabular*}

  \resumesection{Projects}{~}

    White Hat Malware Lab

    \begin{itemize}
      \setlength{\itemsep}{0.15pt}
      \resumelistitem{Personally-developed lab environment for teaching static/dynamic malware analysis techniques to club members.}
      \resumelistitem{Allows for club research on malware attacks,
        antivirus bypasses, reverse-engineering training, and \\ Kali Linux/Metasploit ethical penetration-testing teaching and practice.}
      \resumelistitem{Powered by VMware ESXI, Python Flask, pfSense, and CrowdStrike Hybrid Analysis.}
    \end{itemize}

  \resumesection{White Hat Cybersecurity Club (SLO)}{}

    \begin{itemize}
      \setlength{\itemsep}{0.15pt}
      \resumelistitem{Malware Tech Team Lead – Project founder and leader of a
        20+ member team.} \hfill Fall 2019\textemdash Present
      \resumelistitem{SysAdmin – Administrator of lab server, networking, and
        custom CTF infrastructure.} \hfill Spring 2019\textemdash Present
      \resumelistitem{Webmaster – Developer/Maintainer of club website
        (https://thewhitehat.club).} \hfill Spring 2018\textemdash Spring 2019
      \resumelistitem{Gave technical talks on Virtualization Security, Malware
        Analysis, \\ Web Server Security, Security Question Security, Intro to Networks and the Internet, DNS and DNS Security.}
    \end{itemize}

  \resumesection{Relevant Coursework}{~}

    \vspace{0.6em}
    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l l l}
      Computer Security & Wireless Security & Programming Languages \\
      Computer Networks & Systems Programming & Computer Architecture \\
      Operating Systems & Intro to Computing with Security & Technical Writing \\
    \end{tabular*}

\end{document}
